\textls[-0]{\thetitle}

### 2023-03-31 body.tex
Set out the frame.
Adding TOC.
Added TOC.
Adding front matters.
Add Front Matter

% \begin{abstract}
% \input{abstract}
% \end{abstract}

% \maketitle

\section*{Family Polymorphism by Coq Plugin}

@@

\ifacknowledgments
\section*{Acknowledgments}
We thank the reviewers for their many useful comments.  We thank
Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
for valuable discussions and feedback.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\fi

@@

\section*{Technicality of \TT}

@@

>>>>

\input{frontmatters.tex}

\chapter{Family Polymorphism as Coq Plugin}

@@

@@

\chapter{Technicality of \TT}

@@

% \ifacknowledgments
% \section*{Acknowledgments}
% We thank the reviewers for their many useful comments.  We thank
% Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
% for valuable discussions and feedback.
% This work was supported in part by an Amazon research award on automated
% reasoning.
% The views and opinions expressed are those of the authors and do not necessarily
% reflect the position of any funding agency.
% \fi

### 2023-03-31 frontmatters.tex
Adding frontmatters.
Add Front Matter

% \begin{abstract}
% \input{abstract}
% \end{abstract}

% \maketitle
% adding chapter here

\tableofcontents

>>>>

% Title Page

\vspace*{\fill}
\begin{center}
  \textsc{\Huge \thetitle}
\end{center}

\vspace*{\fill}

\newpage

% Author's Declaration
\vspace*{\fill}

\chapterN{Author's Declaration}

\vspace*{\fill}

\newpage

% Statement of contributions

\vspace*{\fill}

\chapterN{Statement of contributions}

\vspace*{\fill}

\newpage

% Abstract
\vspace*{\fill}
\chapterN{Abstract}

\input{abstract}
\vspace*{\fill}

\newpage

% Acknowledgements

\vspace*{\fill}
\chapterN{Acknowledgments}

We thank Anastasiya Kravchuk-Kirilyuk, Yao Li, Andrew Myers, and Zhixuan Yang
for valuable discussions and feedback.
This work was supported in part by an Amazon research award on automated
reasoning.
The views and opinions expressed are those of the authors and do not necessarily
reflect the position of any funding agency.
\vspace*{\fill}

\newpage
\tableofcontents
